Searching for Software in NSF Awards

### 2023-02-14 paper/paper.qmd
Anonymous submission

---
title: "Searching for Software in NSF Awards"
author:
  - name: "Eva Maxfield Brown"
    email: evamxb@uw.edu
    orcid: 0000-0003-2564-0373
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Lindsey Schwartz"
    email: lsschwar@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Richard Lewei Huang"
    email: lwhuang@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Nicholas Weber"
    email: nmweber@uw.edu
    orcid: 0000-0002-6008-3763
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA

abstract: |
  Software is an important tool for scholarly work, but software produced for research is in many cases not easily identifiable or discoverable. A potential first step in linking research and software is software identification. In this paper we present two datasets to study the identification and production of research software. The first dataset contains almost 1000 human labeled annotations of software production from National Science Foundation (NSF) awarded research projects. We use this dataset to train models that  predict software production. Our second dataset is created by applying the trained predictive models across the abstracts and project outcomes reports for all NSF funded projects between the years of 2010 and 2023. The result is an inferred dataset of software production for over 150,000 NSF awards. We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager

@@

The data used for training, and functions to reproduce these models, are made available via our Python package: [`soft-search`](https://github.com/si2-urssi/eager).

@@

All datasets and predictive models produced by this work are available from our GitHub repository: [`si2-urssi/eager`](https://github.com/si2-urssi/eager).

@@

We thank the USRSSI team, especially Karthik Ram for their input. This material is based upon work supported by the National Science Foundation under Grant 2211275.

>>>>

---
title: "Searching for Software in NSF Awards"
author:
  - name: Anonymous Submission
  # - name: "Eva Maxfield Brown"
  #   email: evamxb@uw.edu
  #   orcid: 0000-0003-2564-0373
  #   affliation:
  #       name: University of Washington Information School
  #       city: Seattle
  #       state: Washington
  #       country: USA
  # - name: "Lindsey Schwartz"
  #   email: lsschwar@uw.edu
  #   affliation:
  #       name: University of Washington Information School
  #       city: Seattle
  #       state: Washington
  #       country: USA
  # - name: "Richard Lewei Huang"
  #   email: lwhuang@uw.edu
  #   affliation:
  #       name: University of Washington Information School
  #       city: Seattle
  #       state: Washington
  #       country: USA
  # - name: "Nicholas Weber"
  #   email: nmweber@uw.edu
  #   orcid: 0000-0002-6008-3763
  #   affliation:
  #       name: University of Washington Information School
  #       city: Seattle
  #       state: Washington
  #       country: USA

abstract: |
  Software is an important tool for scholarly work, but software produced for research is in many cases not easily identifiable or discoverable. A potential first step in linking research and software is software identification. In this paper we present two datasets to study the identification and production of research software. The first dataset contains almost 1000 human labeled annotations of software production from National Science Foundation (NSF) awarded research projects. We use this dataset to train models that  predict software production. Our second dataset is created by applying the trained predictive models across the abstracts and project outcomes reports for all NSF funded projects between the years of 2010 and 2023. The result is an inferred dataset of software production for over 150,000 NSF awards. We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/redacted-for-submission

@@

The data used for training, and functions to reproduce these models, are made available via our Python package: [`redacted`](https://github.com/redacted-for-submission).

@@

All datasets and predictive models produced by this work are available from our GitHub repository: [`redacted`](https://github.com/redacted-for-submission).

@@

Redacted for anonymous submission.
